Promotors' reports on the first draft of the thesis document.

### 2020-03-20 ChapterConclusion/ChapterConclusion.tex
Third review

\chapter{Conclusions and \linebreak future work} \label{chap:concl}

\vfill{}

%In this final chapter, we first summarize the contributions made to both parts of the thesis: \textbf{Part \ref{part:Filter}} and \textbf{Part \ref{part:PA}}. Then, I propose some possible further improvements to extend this work in future research.

@@

Conclusions - Statistical analysis

 We conducted a statistical analysis of a structured errors-in-variables (EIV) estimation problem with correlation to find the first and second moments of its least-squares solution.
This estimation problem occurs in metrology when we estimate the value of a measurand directly from the sensor transient response.
The data-driven estimation of the physical quantity is formulated as a structured EIV problem with correlation that uses the observed transient response to construct both the regression matrix and the regressor.
The real-time implementation of the method uses a recursive least squares algorithm that is simple and has low computational complexity.
The assessment of the uncertainty is done using the estimate bias and variance.

Conclusions - Experimental validation

In this paper we investigated the statistical properties of a data-driven step input estimation method in a real-life application.
The step input estimation method is a structured and correlated errors-in-variables problem that is solved with recursive least squares.
A statistical analysis was conducted using the ordinary least squares condensed notation. 
This statistical analysis of the input estimate provides expressions that approximate the estimation bias and variance assuming that the measurement noise is Gaussian white noise. 
The variance approximation is useful to assess the uncertainty of the input estimate.
In simulation we observed that the mean squared error of the input estimate is close to the theoretical minimum that uses the Cram\'er-Rao lower bound for biased estimators.
Since the data-driven step input estimation method is not statistically efficient, there is room for improvement. This is a topic for future research.
In the practical experiments, the measurement noise is not white.
The noise variance obtained from the sensor steady state response underestimates the measurement noise variance, that was observed 5 dB larger in the power spectrum due to nonlinearities of the sensor.
Considering this difference in the measurement noise variance, we introduced a conservative bound of the measurement noise variance so that the first and second moments of the input estimate are more accurately predicted.
Using the variance approximation, we can assess the uncertainty of the input estimate with respect to the number of samples processed by the data-driven step input estimation method.
The step input estimation method is useful in practical applications where the whiteness assumption of the measurement noise is not fulfilled.

Conclusions - Ramp input

Future work of this research is the practical implementation of the subspace method for real-time measurements.

\begin{comment}
\section{Conclusions - Ramp input}

Future work of this research is the practical implementation of the subspace method for real-time measurements.

\section{Conclusions - Statistical analysis}

 We conducted a statistical analysis of a structured errors-in-variables (EIV) estimation problem with correlation to find the first and second moments of its least-squares solution.
This estimation problem occurs in metrology when we estimate the value of a measurand directly from the sensor transient response.
The data-driven estimation of the physical quantity is formulated as a structured EIV problem with correlation that uses the observed transient response to construct both the regression matrix and the regressor.
The real-time implementation of the method uses a recursive least squares algorithm that is simple and has low computational complexity.
The assessment of the uncertainty is done using the estimate bias and variance.

@@

In this paper we investigated the statistical properties of a data-driven step input estimation method in a real-life application.
The step input estimation method is a structured and correlated errors-in-variables problem that is solved with recursive least squares.
A statistical analysis was conducted using the ordinary least squares condensed notation. 
This statistical analysis of the input estimate provides expressions that approximate the estimation bias and variance assuming that the measurement noise is Gaussian white noise. 
The variance approximation is useful to assess the uncertainty of the input estimate.
In simulation we observed that the mean squared error of the input estimate is close to the theoretical minimum that uses the Cram\'er-Rao lower bound for biased estimators.
Since the data-driven step input estimation method is not statistically efficient, there is room for improvement. This is a topic for future research.
In the practical experiments, the measurement noise is not white.
The noise variance obtained from the sensor steady state response underestimates the measurement noise variance, that was observed 5 dB larger in the power spectrum due to nonlinearities of the sensor.
Considering this difference in the measurement noise variance, we introduced a conservative bound of the measurement noise variance so that the first and second moments of the input estimate are more accurately predicted.
Using the variance approximation, we can assess the uncertainty of the input estimate with respect to the number of samples processed by the data-driven step input estimation method.
The step input estimation method is useful in practical applications where the whiteness assumption of the measurement noise is not fulfilled.

\section*{Future work}
\end{comment}

text

>>>>

\chapter[Conclusions and future work]{Conclusions and \linebreak future work} \label{chap:concl}

%\vfill{}

%In this final chapter, I first summarize the contributions made in the thesis. Then, I propose some possible further improvements to extend this work in future research.

@@

This thesis describes the validation of a signal processing method for metrology applications.
The signal processing method takes the transient step response of a linear time-invariant sensor and provides an estimation of the level of the originating step input.
The signal processing method is a subspace data-driven estimation method and constitutes an alternative to typical sensor response processing approaches based on compensation filters.
Contrary to the compensation filters, this data-driven estimation method is model-independent and reduces the estimation time. 
The reason for the time reduction is the bypassing of the model parameters estimation, which is not performed previously nor simultaneously to the input estimation.
The improvement in speed estimation makes the data-driven method suitable for real-time measurements.

Quantifying the estimation uncertainty was necessary to convince the metrology community of the data-driven method advantages.
The uncertainty assessment is not straightforward.
The data-driven method formulates a minimization problem that is a block-Hankel structured and correlated errors-in-variables (EIV) problem.
The recursive least-squares (LS) solution to the minimization problem enables the online implementation of the method.
The structure and correlation of the EIV problem required research to find the first and second statistical moments of the LS solution.

The first part of the research reported in this thesis deals with the determination of the mean value and the covariance that the LS estimator has when it solves a structured and correlated EIV problem.
The Taylor series expansion of the LS solution permits the study of the expected value of the LS estimate.
The series expansion takes into account the structure of the regression matrix and the correlation between the regression matrix and the regressor.
With the Taylor series expansion, the element-wise treatment is not a strict requirement for the statistical analysis since it is possible to use matrix form in the computations.
As a result, the statistical analysis yielded expressions that approximate the bias and the covariance of the LS estimate for given sample size and perturbation level.
These expressions also help to understand the impact that the different matrix structures and the correlation bring into EIV problems and their solutions.

The LS bias and covariance predictions were validated first by Monte Carlo simulations. 
In the simulations are obtained the empirical statistical moments of the LS estimation, and their predictions calculated using the derived expressions.
The simulations used an extensive set of values in the workspace of the step response sample size and perturbation levels.
The learning obtained from the simulation results is the operating conditions in which the estimation method is effective.
The operation conditions were the data-driven estimation method is effective include a region of signal-to-noise (SNR) near to 40 dB, which is typical in many real-life applications.
This effectiveness near an SNR of 40 dB is a positive indication for the usability of the method in metrology.
Another encouraging result is that the mean squared error of the data-driven method estimate is considerably near to the minimal theoretical variance that is defined by the Cram\'er-Rao lower bound of the formulated EIV problem.

The temperature and mass measurements are adequate for testing the implementation of the method.
These two physical magnitudes are demanded applications in scientific and industrial fields, and there are available sensors of low cost in the market.
The mass measurement demands more effort from the step input estimation method in a real-life application.
Mass measurement sensors are affected by environment vibrations.
Moreover, the mechanical constructions of the weighing sensors increase the order complexity of the sensor model.
A load cell sensor, used as the weighing sensor, has a high order, that in theory, is infinite. 
A non-surprising observation in the implementation of experimental measurements is that the measurement noise collected from the weighing sensor is not Gaussian white noise.
Nevertheless, the implementation of the data-driven step input estimation method showed good performance results under these conditions. 
The estimation method showed robustness against non-white noise and provided acceptable results for system orders selected between 5 and 7.

A third aspect of the conducted research included the exploration of estimating inputs based on different models with signal processing methods. 
A first choice is the affine input model, which is one complexity level higher than the step input.
The exploration demonstrated that the adaptation of the data-driven method with the exponentially weighted recursive LS (EWRLS) is useful to estimate the affine input.
More general than the recursive LS estimator, the EWRLS uses a tuning parameter to select the data samples relevant for the solution computation.

The affine input estimation problem became more interesting because the application of the affine input to a weighing sensor turns the LTI system into a time-varying (TV) system. 
The adaptive data-driven affine input estimation method was simulated under different assumptions and showed robustness when processing time-varying sensor responses.
Two other estimation methods are used as a reference to compare the results of the adaptive method.
These methods are a maximum-likelihood (ML) estimator based on local optimization and a previously reported digital time-varying filter.
The adaptive affine input estimation method outperformed the time-varying filter by presenting lower estimation time, and the ML method by requiring less computational effort.

\section*{Future work}

The use of model independent signal processing methods is a research field that surely will produce interesting results in the near future. 
With the increasing power of digital signal processors, the design of new methods is an opportunity that cannot be disregarded.

The data-driven method studied in this thesis is one example of an alternative to dynamic measurements under a different paradigm.
With respect to this method, one conclusion of the analysis presented can be that the data-driven step input estimation method is not statistically efficient because the estimation shows bias.
A topic for future research is the efficiency increase, perhaps by designing fast and optimal estimators for structured and correlated EIV problems.

On the other hand, for model-based estimation methods, such as the described ML method that has a high computational cost, there is a need also for efficient implementations to enable online optimization in receding-horizon schemes. 
With such efficient methods, the practical implementation of the ML methods can become feasible for real-time measurements.

\begin{comment}
\section{Conclusions - Statistical analysis}

 We conducted a statistical analysis of a structured errors-in-variables (EIV) estimation problem with correlation to find the first and second moments of its least-squares solution.
This estimation problem occurs in metrology when we estimate the value of a measurand directly from the sensor transient response.
The data-driven estimation of the physical quantity is formulated as a structured EIV problem with correlation that uses the observed transient response to construct both the regression matrix and the regressor.
The real-time implementation of the method uses a recursive least-squares algorithm that is simple and has low computational complexity.
The assessment of the uncertainty is done using the estimate bias and variance.

@@

In this paper we investigated the statistical properties of a data-driven step input estimation method in a real-life application.
The step input estimation method is a structured and correlated errors-in-variables problem that is solved with recursive least-squares.
A statistical analysis was conducted using the ordinary least-squares condensed notation. 
This statistical analysis of the input estimate provides expressions that approximate the estimation bias and variance assuming that the measurement noise is Gaussian white noise. 
The variance approximation is useful to assess the uncertainty of the input estimate.
In simulation we observed that the mean squared error of the input estimate is close to the theoretical minimum that uses the Cram\'er-Rao lower bound for biased estimators.
Since the data-driven step input estimation method is not statistically efficient, there is room for improvement. This is a topic for future research.
In the practical experiments, the measurement noise is not white.
The noise variance obtained from the sensor steady state response underestimates the measurement noise variance, that was observed 5 dB larger in the power spectrum due to nonlinearities of the sensor.
Considering this difference in the measurement noise variance, we introduced a conservative bound of the measurement noise variance so that the first and second moments of the input estimate are more accurately predicted.
Using the variance approximation, we can assess the uncertainty of the input estimate with respect to the number of samples processed by the data-driven step input estimation method.
The step input estimation method is useful in practical applications where the whiteness assumption of the measurement noise is not fulfilled.

\section{Conclusions - Ramp input}

Future work of this research is the practical implementation of the subspace method for real-time measurements.
\end{comment}

### 2020-03-20 ChapterExperimentalValidation/ChapterExperimentalValidation.tex
Third review

\begin{quote}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Experimental validation of a data-driven step input estimation method for dynamic measurements", IEEE Transactions on Instrumentation and Measurement Journal, 2019, doi: 10.1109/TIM.2019.2951865. \nocite{QuintanaTIM} }\vfill{}
\end{quote}

 \vfill{}

@@

The influence of the input is observed in the sensor output, and thus it makes sense to estimate the input using the sensor response.
When the sensor reaches its steady-state, the input is a straightforwardly estimated from the sensor output making use of the sensor static gain.
To obtain a fast estimation, the sensor transient response must be considered instead of the steady state response.

A common approach is to filter the sensor transient response with another dynamic system to reduce the sensor transient time by inverting the sensor dynamics.
To design such a compensator system it is necessary a sensor model.
A different approach uses digital signal processing methods that are independent of the sensor model.
One of these methods is the data-driven method that estimates the unknown level of step inputs by processing the sensor step response. 
To assess the uncertainty of the data-driven step input estimation method, a experimental validation of this method was conducted in a real-life metrology application. 
This chapter describes the measurement experiments with a weighing sensor system and discuss the results observed.
The results are put in perspective to simulations and consider the measurement noise that is additive to the response of the sensor.

The experimental results validate the data-driven step input estimation method, and indicate in which intervals of SNR and sample size the effectiveness of the method is guaranteed.

>>>>

\begin{quote}
\vspace{-0.75cm}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Experimental validation of a data-driven step input estimation method for dynamic measurements", IEEE Transactions on Instrumentation and Measurement Journal, 2019, doi: 10.1109/TIM.2019.2951865. \nocite{QuintanaTIM} }\vfill{}
\end{quote}

%\vfill{}

@@

The input excitation influences the sensor output, and thus it makes sense to estimate the input using the sensor response.
When the sensor reaches its steady-state, the input is a straightforwardly estimated from the sensor output making use of the sensor static gain.
The sensor transient response must be considered, instead of the steady state response, to obtain a fast input estimation.

A common approach is to filter the sensor transient response with another dynamic system that inverts the sensor dynamics, aiming to compensate the sensor transient time.
It is necessary to have a sensor model to design a compensator system. 
A different approach uses digital signal processing methods that are independent of the sensor model.
One of these methods is the data-driven method that estimates the unknown level of step inputs by processing the sensor step response. 
To assess the uncertainty of the data-driven step input estimation method, it processed step responses in a real-life metrology application. 
This chapter describes the measurement experiments with a weighing sensor system and discusses the results observed.
The results are put in perspective to simulations and consider the measurement noise that is additive to the response of the sensor.

The experimental results validate the data-driven step input estimation method and indicate in which intervals of SNR and sample size the method is reliable.

### 2020-03-20 ChapterIntroduction/ChapterIntroduction.tex
Third review

\vfill{}

@@

% Context:Compensation systems, 
One approach to get a fast input estimation is filtering the sensor transient response with another dynamical system that inverts the dynamics of the sensor.
The filter output is an input estimate that compensates for the measurement time.
The transient duration of the compensation filter should be smaller than that of the sensor.
The compensator is designed after a sensor model to deconvolve the sensor response.

@@

% Context:Data-driven methodology
% The philosophy behind the estimation method is avoiding the explicit identification of a system model from input-output data and estimating directly the input from the transient response.
The main advantage of the data-driven input estimation method is that it does not identify the sensor model, but instead, it directly estimates the input. 
The direct estimation differs from the standard two-stage methodology, that first identifies the sensor model and later estimates the input.
In this approach, the output-error (OE) problem is converted into an EIV problem that is harder to solve, but the RLS solution is easy to compute.
The range of application of the data-driven input estimation method is extensive because it is independent of the sensor model.
The main disadvantage of the data-driven input estimation method is that its stochastic properties are not straightforwardly evident. 
It is more complex to find the stochastic properties of EIV problems when they have structure and correlation.
% Moreover, the online uncertainty assessment may not be feasible and we have to rely on confidence bounds.

% Problem under study: Dynamic measurements
% DM:Uncertainty assessment of data-driven input estimation methods
% DM:Experimental validation of the data-driven step input estimation method
The estimation uncertainty assessment is needed to validate the estimation methods for metrology applications.
The uncertainty of the data-driven step input estimation method \citep{Markovsky15ieee} is unknown.
The estimation bias and variance define the estimation uncertainty \citep{Pintelon12Book}, and they can be obtained by conducting an elementwise statistical analysis. 
The validation of the step input estimation method requires also to demonstrate its effectiveness on real-life measurements.
Temperature and mass sensors are suitable devices to make real-life measurement experiments.
One challenge of using real-life data is that the noise may not fulfill the whiteness assumption considered in the estimation problem formulation and the statistical analysis.
The simulation and experimental results permit to compare the performance of the step input estimation method.

% DM:Estimation of affine input parameters
The ideas behind the step input estimation method raise the curiosity towards the design of estimation methods for other input models.
One of these input models is the ramp.
The dynamic weighing, performed in conveyor systems, also motivates the ramp input estimation method.
The dynamic weighing estimates the mass of materials or products during their transportation.
Ideally, when the conveyor belt transports the materials at a constant speed, i.e., the weighing sensor is excited with a ramp profile. 
The ramp is an affine input model that consists of two parameters: the slope and the interception.
The slope depends on the applied mass and can be used to estimate it from the transient response.
An adaptation of the step input estimation method can estimate the parameters of affine inputs.

% general preview of the thesis contents
This thesis describes three works initiated after the data-driven step input estimation method.
The first work is a statistical analysis to elucidate the bias and the covariance of the estimate that this method provides.
These statistical moments build the estimation uncertainty that appraises the effectiveness of the method.

@@

This thesis describes research work initiated after the data-driven step input estimation method.
This method aims for metrology applications but it lacked an uncertainty assessment, and, therefore, its appropriateness was questionable.
The first research work conducted was a statistical analysis to elucidate the bias and the covariance of the estimate that the data-driven step input estimation method provides.
After obtaining these statistical moments, the estimation uncertainty was assessed, and the effectiveness of the method was evaluated.
The second research work was a series of experiments conducted to validate the data-driven step input estimation method in real-life applications.
The experiments were realizations of the step input excitation using temperature and mass sensors.
The step input estimation method showed robustness when the measurement noise is not Gaussian and white, as it was assumed in the theoretical analyses.
The third research work conducted was the estimation of affine input parameters following the data-driven approach for real-time applications. 
The data-driven method uses exponential weighing in the recursive least-squares solution of a structured errors-in-variables problem, to give preference to recent samples over the older samples.
The methodology and performance of the data-driven affine input estimation method were compared to those of a maximum likelihood method based.

@@

In the proposed data-driven method for the estimation of the affine input \citep{QuintanaMEAS},
the affine input is parameterized as a straight line model where the slope and the interception are the parameters of interest.
The data-driven affine input estimation method formulates a structured errors-invariables (EIV) problem, similar to the one fourmulated for the step input estimation.
An exponential weight is added to the recursive least-squares.
This is a forgetting factor that considers that the newer samples are more relevant for the input parameters estimation.
The data-driven affine input estimation method is a recursive algorithm that can be implemented in real-time since it has low computational cost.

>>>>

%\vfill{}

@@

% Context:Compensation systems, 
One approach to get a fast input estimation is filtering the sensor transient response with another dynamical system that inverts the dynamics of the sensor.
The filter output is an input estimate that compensates for the time span of the sensor transient state.
The transient duration of the compensation filter should be smaller than that of the sensor.
The compensator is designed after a sensor model to deconvolve the sensor response.

@@

% Context:Data-driven methodology
% The philosophy behind the estimation method is avoiding the explicit identification of a system model from input-output data and estimating directly the input from the transient response.
The main advantage of the data-driven step input estimation method is that it does not identify the sensor model, but instead, it directly estimates the input. 
The direct estimation differs from the standard two-stage methodology, that first identifies the sensor model and later estimates the input.
In this approach, the output-error (OE) problem is converted into an EIV problem that is harder to solve, but the RLS solution is easy to compute.
The range of application of the data-driven input estimation method is extensive because it is independent of the sensor model.
The main disadvantage of the data-driven input estimation method is that its stochastic properties are not straightforwardly evident. 
It is more complex to find the stochastic properties of EIV problems when they have structure and correlation.
% Moreover, the online uncertainty assessment may not be feasible and we have to rely on confidence bounds.

% Problem under study: Dynamic measurements
% DM:Uncertainty assessment of data-driven input estimation methods
% DM:Experimental validation of the data-driven step input estimation method
The estimation uncertainty assessment is needed to validate the estimation methods for metrology applications.
The uncertainty of the data-driven step input estimation method \citep{Markovsky15ieee} is unknown.
The estimation bias and variance define the estimation uncertainty \citep{Pintelon12Book}, and they can be obtained by conducting an elementwise statistical analysis. 
The validation of the step input estimation method requires also to demonstrate its effectiveness on real-life measurements.
Temperature and mass sensors are suitable devices to make real-life measurement experiments.
One challenge of using real-life data is that the noise may not fulfill the whiteness assumption considered in the estimation problem formulation and the statistical analysis.
The simulation and experimental results permit to observe and compare the performance of the step input estimation method.

% DM:Estimation of affine input parameters
The ideas behind the step input estimation method raise the curiosity towards the design of estimation methods for other input models.
One of these input models is the ramp.
The dynamic weighing, performed in conveyor systems, also motivates the ramp input estimation method.
The dynamic weighing estimates the mass of materials or products during their transportation.
Ideally, when the conveyor belt transports the materials at a constant speed, i.e., the weighing sensor is excited with a ramp profile. 
The ramp is an affine input model that consists of two parameters: the slope and the intercept.
The slope depends on the applied mass and can be used to estimate it from the transient response.
An adaptation of the step input estimation method can estimate the parameters of affine inputs.

% general preview of the thesis contents
%This thesis describes three works initiated after the data-driven step input estimation method.
%The first work is a statistical analysis to elucidate the bias and the covariance of the estimate that this method provides.
%These statistical moments build the estimation uncertainty that appraises the effectiveness of the method.

@@

This thesis describes research work initiated after the data-driven step input estimation method.
This method aims for metrology applications but it lacked an uncertainty assessment, and, therefore, its appropriateness was questionable.
The first research work conducted was a statistical analysis to elucidate the bias and the covariance of the estimate that the data-driven step input estimation method provides.
After obtaining these statistical moments, the estimation uncertainty was assessed, and thus, the effectiveness of the method was appraised.
The second research work was a series of experiments conducted to validate the data-driven step input estimation method in real-life applications.
The experiments were realizations of the step input excitation using temperature and mass sensors.
The step input estimation method showed robustness when the measurement noise is not Gaussian and white, as it was assumed in the theoretical analyses.
The third research work conducted was the estimation of affine input parameters following the data-driven approach for real-time applications. 
The data-driven method uses exponential weighing in the recursive least-squares solution of a structured errors-in-variables problem, to give preference to recent samples over the older samples.
The methodology and performance of the data-driven affine input estimation method were compared to those of a maximum likelihood method based.

@@

In the proposed data-driven method for the estimation of the affine input \citep{QuintanaMEAS},
the affine input is parameterized as a straight line model where the slope and the intercept are the parameters of interest.
The data-driven affine input estimation method formulates a structured errors-invariables (EIV) problem, similar to the one fourmulated for the step input estimation.
An exponential weight is added to the recursive least-squares.
This is a forgetting factor that considers that the newer samples are more relevant for the input parameters estimation.
The data-driven affine input estimation method is a recursive algorithm that can be implemented in real-time since it has low computational cost.

### 2020-03-20 ChapterRampInput/ChapterRampInput.tex
Third review

\begin{quote}
\emph{The results of this chapter were published in Quintana Carapia, G., and Markovsky, I.,
"Input parameters estimation from time-varying measurements", Measurement Journal, Vol. 153, 2020,
ISSN 0263-2241, doi:10.1016/j.measurement.2019.107418. \nocite{QuintanaMEAS} }\vfill{}
\end{quote}

\vfill{}

@@

The goal of a measurement is to accurately estimate the input value using the sensor transient response.
Here we consider the case where the input might vary during the measurement.
The simplest case is when the input changes with a constant rate, and is described with an affine function.
The inputs that vary at a constant rate activate the sensor gradually. 
An affine input estimation method is needed to estimate the slope and the intercept parameters of the affine function.

This chapter describes two signal processing methods for estimating affine input parameters.
These methods are a data-driven subspace method and a maximum-likelihood (ML) estimation method based on local-optimization.
The subspace is a recursive method independent of the sensor model, and the ML method iteratively minimizes a cost function using a simulated sensor response in a receding time horizon.

In this chapter, the dynamic weighing is chosen as an implementation example.
The dynamic weighing of an affine input is an interesting metrology application because the affine input turns a linear time-invariant sensor model into a time-varying sensor model.
The affine input estimation methods provide an insight on the properties of the dynamic measurement of time-varying inputs.

The effectiveness and the uncertainty of the methods are evaluated with simulation studies.
The uncertainty is assessed, for the subspace method, using a Taylor series expansion of the exponentially weighted recursive least-squares estimate, and
for the ML method, using the derivatives of the residual error obtained from the to-be-minimized cost function.

>>>>

\begin{quote}
\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., and Markovsky, I.,
"Input parameters estimation from time-varying measurements", Measurement Journal, Vol. 153, 2020,
ISSN 0263-2241, doi:10.1016/j.measurement.2019.107418. \nocite{QuintanaMEAS} }\vfill{}
\end{quote}

%\vfill{}

@@

The goal of any measurement is accurately estimating the input using the response of the sensor in the transient state.
Here we consider the case where the input varies during the measurement.
The simplest case is when the input changes with a constant rate, such as being described with an affine function.
The inputs that vary at a constant rate activate the sensor gradually. 
An affine input estimation method is needed to estimate the slope and the intercept parameters of the affine function.

This chapter describes two signal processing methods for estimating affine input parameters.
These methods are a data-driven subspace method and a maximum-likelihood (ML) estimation method based on local optimization.
The subspace is a recursive method independent of the sensor model, and the ML method iteratively minimizes a cost function using a simulated sensor response in a receding time horizon.

In this chapter, the dynamic weighing is an implementation example.
The dynamic weighing of an affine input is a demanding metrology application because the affine excitation turns the linear time-invariant weighing sensor into a time-varying system.
Then, the affine input estimation methods provide insight into the properties of the dynamic measurement of time-varying inputs.

The effectiveness and uncertainty of the proposed methods are evaluated with simulation studies.
The uncertainty is assessed, for the adaptive data-driven method, using a Taylor series expansion of the EWRLS estimate, and
for the ML method, using the derivatives of the residual error obtained from the to-be-minimized cost function.

### 2020-03-20 ChapterStatisticalAnalysis/ChapterStatisticalAnalysis.tex
Third review

\begin{quote}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Bias and covariance of the least-squares estimate in a structured errors-in-variables problem", Computational Statistics & Data Analysis journal, Vol. 144, 2020, ISSN 0167-9473, doi:10.1016/j.csda.2019.106893. \nocite{QuintanaCSDA} }\vfill{}
\end{quote}

\vfill{}

@@

The linear estimation problems with perturbation in both the regression matrix and the regressor are errors-in-variables (EIV) problems.
To evaluate the properties of the solution to an EIV problem it is often required to calculate the statistical moments of the estimate.
The calculation of the estimate statistical moments demands a larger effort when the regression matrix of a EIV problem is structured, and when is correlated to the regressor.

Structured total least-squares and structured total maximum likelihood are two examples of methods that solve structured EIV problems, but that require large computational resources.
For online applications where a real-time solution of the structured EIV problem is desired, the recursive least-squares (RLS) method is a suboptimal but computationally cheaper estimator.

To obtain the statistical moments of the RLS estimation for a structured and correlated EIV problem, and to assess the estimation uncertainty, that have not been obtained before, a statistical analysis was conducted.

This chapter describes the methodology and the results of the statistical analysis.
The mathematical expectation of the RLS estimate, approximated by a second-order Taylor series expansion, allows a quantification of the first and second-order moments of the LS estimate.
The results of the statistical analysis provide an insight of the impact that the structure of the regression matrix and the correlation between the regression matrix and the regressor perturbations have on the uncertainty of the RLS estimate.

>>>>

\begin{quote}
\vspace{-0.5cm}
\emph{The results of this chapter were published in Quintana Carapia, G., Markovsky, I. Pintelon, R., Csurcsia, P.Z., and Verbeke, D., "Bias and covariance of the least-squares estimate in a structured errors-in-variables problem", Computational Statistics & Data Analysis journal, Vol. 144, 2020, ISSN 0167-9473, doi:10.1016/j.csda.2019.106893. \nocite{QuintanaCSDA} }\vfill{}
\end{quote}

%\vfill{}

@@

The linear estimation problems with perturbation in both the regression matrix and the regressor are errors-in-variables (EIV) problems.
It is required to calculate the statistical moments of the estimate to evaluate the properties of the solution of an EIV problem.
The calculation of the estimate statistical moments demands a more considerable effort when the regression matrix of an EIV problem is structured, and when the regression matrix and the regressor are correlated.

Structured total least-squares and structured total maximum likelihood are two examples of methods that solve structured EIV problems, but that require large computational resources.
For online applications, where a real-time solution of the structured EIV problem is imperative, the recursive least-squares (RLS) method provides a suboptimal but computationally cheaper online solution.

Statistical analysis is indispensable to obtain the statistical moments of the RLS solution for a structured and correlated EIV problem, and to assess the estimation uncertainty.
This chapter describes the methodology and the results of the statistical analysis.
The mathematical expectation of the RLS estimate, approximated by a second-order Taylor series expansion, allows a quantification of the first and second-order moments of the LS estimate.
The statistical analysis results provide insight into the impact that the structure of the regression matrix and its correlation with the regressor has on the uncertainty of the RLS estimate.

### 2020-03-20 Extras/Summary.tex
Third review

\vspace{-1.2cm}

Sensors are dynamical systems, and their input excitations are the physical quantities. 
The input must be estimated during the sensor transient state to expedite the measurements. 
Otherwise, users have to wait for the sensor steady state when the response is proportional to the input through the sensor static gain. 
One approach to get fast input estimation is filtering the sensor transient response with another dynamical system aiming to compensate the estimation time by reconstructing the input. 
Another approach is processing the transient response on a digital signal processor (DSP). 
Contrary to model-based compensators, DSPs allow model-free methods that can reduce the measurement time.

There exists a model-free method that directly estimates the step input level from the sensor step response. 
The formulation of this method is a Hankel-structure errors-in-variables (EIV) problem, where the regression matrix and the regressor are correlated.
The structured EIV problem is solved with recursive least-squares to allow for real-time implementation.
The range of application of this step input estimation method is broad because of its sensor model independence.

The stochastic properties of the step input estimation method are unknown and are not straightforwardly evident.
To validate the method for metrology applications, we studied the estimation uncertainty by doing a statistical analysis of the step input estimation.
The estimation bias and variance builds the estimation uncertainty.
The statistical analysis of the estimation method yields expressions that predict the estimate first and second moments.

>>>>

\vspace{-1.5cm}

Sensors are dynamical systems, and the physical quantities are their input excitations. 
The input magnitude must be estimated during the sensor transient state to expedite the measurements. 
Otherwise, users have to wait for the sensor steady state when the response is proportional to the input. 
In this case, the proportionality constant is the sensor static gain. 
One approach to get fast input estimation is filtering the sensor transient response with another dynamical system aiming to compensate the estimation time by regenerating the input. 
Another approach is processing the transient response on a digital signal processor (DSP). 
Contrary to model-based compensators, DSPs allow model-free methods that can reduce the measurement time.

There exists a data-driven method that directly estimates the step input level from the sensor step response. 
The formulation of this method is a Hankel-structure errors-in-variables (EIV) problem, where the regression matrix and the regressor are correlated.
The structured EIV problem is solved with recursive least-squares to allow for real-time implementation.
The range of application of this step input estimation method is broad because of its independence from the sensor model .

The stochastic properties of the step input estimation method are unknown and are not straightforwardly evident.
To validate the method for metrology applications, we studied the estimation uncertainty by doing a statistical analysis of the step input estimation.
The estimation bias and variance build the estimation uncertainty.
The statistical analysis of the estimation method yields expressions that predict the estimation first and second moments and enable the uncertainty assessment.
